\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
Fixed trial numbers

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (see section \ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of 5700 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).

>>>>

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (see section \ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of approximately 5000 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).
